Data_visualization

### 2018-08-06 Rmd/Data_visualization.Rmd
changes

#changing non_focal species name
caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

@@

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("Flower"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Flower"),]

>>>>

#changing non_focal species name
caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

@@

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))

@@

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]
